### 2013-03-28 doc/sosp13/evaluation.tex
UTS text

\paragraph{Putting it all together with Unbalanced Tree Search in
    memory (UTS).}
We now show the overall performance of \Grappa running UTS.
Figure~\ref{fig:grappa-uts}. The point of this experiment is to
demonstrate whether \Grappa's context switching and communication layers can in fact
be used together, while balancing workload, to run an irregular application efficiently. 
We look at two classes of trees, T1x and T3x, from the
original benchmark. T1x trees are very shallow and wide, while T3x
trees are very deep. When the access to each vertex is a random
access, the critical path to search T3x trees is very long. On such
trees, we do not expect there to be sufficient concurrency for any
system, including \Grappa, to achieve high throughput. \TODO{plot it
    if time}. To verify this, at the 16-node data point, the average active tasks per
core over the search is 775 and 13 for T1XL and T3L, respectively.

@@

\begin{figure}[ht]
    \begin{center}
      \includegraphics[width=0.5\textwidth]{results/benchmarks.pdf}
    \end{center}
    \caption{Comparing \Grappa with XMT, hand-tuned MPI and UPC.}
%bar chart, one set of bars per benchmark, one bar per system. runtime normalized to grappa.
    \label{fig:grappa-comparisons}
\end{figure}

>>>>

\paragraph{Putting it all together with Unbalanced Tree Search in memory
(UTS).} Figure~\ref{fig:grappa-uts} shows the overall performance of \Grappa
running UTS. The point of this experiment is to demonstrate whether \Grappa's
context switching and communication layers can in fact be used together, while
balancing workload, to run an irregular application efficiently. We look at two classes of trees, T1 and T3, from the original benchmark. T1
trees are very shallow and wide (i.e., significant parallel slack), while T3
trees are very deep (i.e., little parallel slack). When the access to each
vertex is a random access, the critical path to search T3 trees is very long,
hence the low performance and scalability. On such trees, we do not expect there to be
sufficient concurrency for any system, including \Grappa, to achieve high
throughput --- at the 16-node data point, the average active
tasks per core over the search is 775 and 13 for T1 and T3, respectively. On the other hand \Grappa performs and scales very well for T1 trees.

@@

\begin{figure}[ht]
    \begin{center}
      \includegraphics[width=0.5\textwidth]{results/benchmarks.pdf}
    \end{center}
    \caption{Comparing \Grappa with XMT, hand-tuned MPI and UPC.}
    \label{fig:grappa-comparisons}
\end{figure}
